---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SaltsR

<!-- badges: start -->
<!-- badges: end -->

SaltsR is a data science tool to aid scientists, researchers, conservators and managers of cultural heritage that are interested in protecting heritage from salt weathering.

KIK-IRPA PREDICT: https://predict.kikirpa.be/

Details of the calculation: https://www.nature.com/articles/s41597-022-01445-9 

Salt Wiki: https://www.saltwiki.net/index.php/Home

ECOS – RUNSALT : http://science.sdf-eu.org/runsalt/

MDCS / Monument Diagnosis and Conservation System : https://mdcs.monumentenkennis.nl/


## Installation

You can install the development version of SaltsR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("BhavShah01/SaltsR")
```

```{r example}
library(SaltsR)
```



