---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SaltsR

<!-- badges: start -->
<!-- badges: end -->

SaltsR is a data science tool designed to support scientists, researchers, conservators, and heritage managers in protecting cultural heritage from salt weathering. It corrects ion chromatography data for use with the Runsalt application (Price 2000; Bionda 2005), based on calculations from [Godts et al. 2022](https://www.nature.com/articles/s41597-022-01445-9). Additionally, Runsalt output files can be uploaded to the tool to generate graphical visualisations.

For the most up-to-date calculations, please use the [Salts Content Calculator](https://predict.kikirpa.be/index.php/tools/moisture-and-salt-sample-data-analysis-tool/).

- [Runsalt software](http://science.sdf-eu.org/runsalt/): Prediction of salt mixture behaviour under changing climate conditions using the ECOS thermodynamic model.
- [KIK-IRPA PREDICT tools](https://predict.kikirpa.be/index.php/tools/): Suite of calculators for hygroscopic moisture content, ion balance, and climate data visualisation.
- [SaltsR R package](https://bhavshah01.github.io/SaltsR/): Data science tools in development for interoperability with Runsalt software.
- [SaltsR Online Application](https://oceanonline.shinyapps.io/SaltsRApp/): Online version of SaltsR to use the package’s functionality. 


**Disclaimer** - this tool is under development and the authour does not take any responsibilty.


## Typical Workflow

-   Upload ion chromatography data for the Runsalt application.

-   Return output for the Runsalt application.

-   Review visualisations and tables.

-   Export analytical results.

## Online

Online version of SaltsR package. You can use the interactive SaltsR application in a web browser:

-   [SaltsR Online Application](https://oceanonline.shinyapps.io/SaltsRApp/)

<https://oceanonline.shinyapps.io/SaltsRApp/>




## SaltsR Installation

You can install the development version of SaltsR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("BhavShah01/SaltsR")
```

```{r example}
library(SaltsR)
```

## Load the Application

[SaltsR Online Application](https://oceanonline.shinyapps.io/SaltsRApp/)

The SaltsR package provides an application to test its calculations. This interactive tool allows you to evaluate the package's output using ion chromatography data.

To launch the application, simply run the following command in R:

``` r
runSaltsR_app()
```

This will open the SaltsR application, where you can input your ion chromatography data and use the package's functionality.


