---
title: "SaltsR"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Install and load 

``` r
install.packages("pak")
pak::pak("BhavShah01/SaltsR")
```

```{r}
library(SaltsR)
```

## Application

[SaltsR Online Application](https://oceanonline.shinyapps.io/SaltsRApp/)

The SaltsR package provides an application to test its calculations. This interactive tool allows you to evaluate the package's output using ion chromatography data.

To launch the application, simply run the following command in R:

``` r
runSaltsR_app()
```

This will open the SaltsR application, where you can input your ion chromatography data and explore the package's functionality.


## Salt balance function

Use the function below with the following inputs to perform a salt balance. The full outputs of the function are shown underneath.

For the most up-to-date calculations, please use the [Salts Content Calculator](https://predict.kikirpa.be/index.php/tools/moisture-and-salt-sample-data-analysis-tool/).

Please raise issues with the SaltsR calculations on the [Github issues page](https://github.com/BhavShah01/SaltsR/issues).

``` r
fun_salt_balance(sample_name = "Example",
                 dry_g = 1,
                 water_ml = 100,
                 chloride_ppm = 50,
                 nitrate_ppm = 30,
                 sulfate_ppm = 20,
                 sodium_ppm = 40,
                 potassium_ppm = 10,
                 calcium_ppm = 15,
                 magnesium_ppm = 5)
```

```{r}
fun_salt_balance(sample_name = "Example",
                 dry_g = 1,
                 water_ml = 100,
                 chloride_ppm = 50,
                 nitrate_ppm = 30,
                 sulfate_ppm = 20,
                 sodium_ppm = 40,
                 potassium_ppm = 10,
                 calcium_ppm = 15,
                 magnesium_ppm = 5) |>
dplyr::glimpse()

```

