---
title: "SaltsR Application"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SaltsR)
library(dplyr)
library(ggplot2)
```


## Online

You can use the interactive SaltsR application in a web browser:

-   [SaltsR Online Application](https://oceanonline.shinyapps.io/SaltsRApp/)

<https://oceanonline.shinyapps.io/SaltsRApp/>


## SaltsR Installation

You can install the development version of SaltsR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("BhavShah01/SaltsR")
```

```{r example}
library(SaltsR)
```

## Load the Application

The SaltsR package provides an application to test its calculations. This interactive tool allows you to evaluate the package's output using ion chromatography data.

To launch the application, simply run the following command in R:

``` r
runSaltsR_app()
```

This will open the SaltsR application, where you can input your ion chromatography data and use the package's functionality.

**Disclaimer** - this tool is under development and the authour does not take any responsibilty.
