---
title: "SaltsR Application"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SaltsR)
library(dplyr)
library(ggplot2)
```


- [Runsalt software](http://science.sdf-eu.org/runsalt/): Prediction of salt mixture behaviour under changing climate conditions using the ECOS thermodynamic model.
- [KIK-IRPA PREDICT tools](https://predict.kikirpa.be/index.php/tools/): Suite of calculators for hygroscopic moisture content, ion balance, and climate data visualisation.
- [SaltsR R package](https://bhavshah01.github.io/SaltsR/): Data science tools in development for interoperability with Runsalt software.

This tool is designed for data analysis and modelling of salt behaviour in cultural heritage materials. Calculations are based on [Godts et al. 2022](https://www.nature.com/articles/s41597-022-01445-9).

For the most up-to-date calculations, please use the [Salts Content Calculator](https://predict.kikirpa.be/index.php/tools/moisture-and-salt-sample-data-analysis-tool/).

## Typical Workflow

-   Upload ion chromatography data.

-   Return output for the Runsalt application.

-   Review visualisations and tables.

-   Export analytical results.

## Online

You can use the interactive SaltsR application in a web browser:

-   [SaltsR Online Application](https://oceanonline.shinyapps.io/SaltsRApp/)

<https://oceanonline.shinyapps.io/SaltsRApp/>


## SaltsR Installation

You can install the development version of SaltsR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("BhavShah01/SaltsR")
```

```{r example}
library(SaltsR)
```

## Load the Application

The SaltsR package provides an application to test its calculations. This interactive tool allows you to evaluate the package's output using ion chromatography data.

To launch the application, simply run the following command in R:

``` r
runSaltsR_app()
```

This will open the SaltsR application, where you can input your ion chromatography data and use the package's functionality.

**Disclaimer** - this tool is under development and the authour does not take any responsibilty.
